Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-19 manuscript/climate_sensitivity_SI.Rmd
Fig. S3 caption
#100

\newpage
![Figure S3: **PLACEHOLDER** ](tables_figures/publication/independent_variables_by_species.png)

>>>>

\newpage
![Figure S3: **Distribution of independent variables by species.** Species that are assigned the same letter are not significantly different from each other with regard to the tested variable. ](tables_figures/publication/independent_variables_by_species.png)
